Hierarchy Builder

### 2020-04-27 coqws/easychair.tex
minor

\paragraph{A hierarchy with a diamond in 50 lines}

@@

For space constraints we omit the declaration
of the green arrows (Figure 1) which are alternative interfaces
called factories. They provide specialized interfaces to build structures for others.
Factories are used to accommodate the insertion of
intermediate structures in a hierarchy without breaking user code, as we all
as to implement shortcuts: the factory to build a \coq{Ring} from \coq{Type}
(rightmost green arrow)
can omit the one for the commutativity of the addition, since it is implied
by the other axioms~\cite{nearrings}.
\bibliography{biblio}

>>>>

\paragraph{Example: A hierarchy with a diamond in \HB{}}

@@

For space constraints we omit the declaration
of the green arrows in Figure 1 which are alternative interfaces
called factories. They provide specialized interfaces to
build structures for others.
Factories are used to accommodate the insertion of
intermediate structures in a hierarchy without breaking user code, as we all
as to implement shortcuts: the factory to build a \coq{Ring} from \coq{Type}
(rightmost green arrow)
can omit the commutativity axiom of the addition, since it is implied
by the other axioms~\cite{nearrings}.
\bibliography{biblio}
